Untitled

### 2024-02-05 MSR.rmd
Update

>>>>

# Bab 3

![](images/clipboard-2906850533.png){width="302"}

## Bernoulli

![](images/clipboard-1833550608.png){width="391"}

```{r}
i <- 1000
p <- .65
X <- runif(i)
Y <- NULL
for (z in 1:i) ifelse (X[z] <= p, Y[z] <- 1, Y[z] <- 0)
(tabel <- table(Y)/length(Y))
barplot(tabel, main="Bernoulli")

i <- 1000
p <- .65
X <- runif(i)
Y <- (X <= p)+0
(tabel <- table(Y)/length(Y))
barplot(tabel, main="Bernoulli")
```

## Seragam Diskrit

![](images/clipboard-958172702.png){width="443"}

```{r}
i <- 1000 
N <- 4
X <- runif(i) 
DU <- NULL
for (z in 1:i){
  if (X[z]<=1/N) DU[z]<-1
    else if (X[z]<=2/N) DU[z]<-2  
    else if (X[z]<=3/N) DU[z]<-3
  else DU[z] <- 4 
}
(tabel <- table(DU)/length(DU)) 
barplot(tabel, main="Seragam Diskret")
```
